Test data

### 2022-07-17 Shiny/Test/Flexdashboard test.Rmd
Plot and explanation. ifelse() rewrite.

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl, flexdashboard)

@@

    # Creating plotly plot
    output$plotlyplot <- renderPlotly(
      ggplotly(lonnplot())
    )
    output$htmlplot <- renderPlot(
      lonnplot()
    )
  })
```

@@

@@

>>>>

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl, flexdashboard, MetBrewer)

@@

    # Creating plotly plot
    output$plotlyplot <- renderPlotly(
      ggplotly(lonnplot())
    )

    # Creating ggplot
    output$htmlplot <- renderPlot(
      lonnplot()
    )

    # Creating fancier plot
    fancyplot <- reactive(
      htmldata() |> 
        select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                    label_dollar(prefix = "? "))
      ) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
    )

    output$fancyplot <- renderPlotly(
      ggplotly(fancyplot())
    )
  })

@@

Please upload an html copy of annual accounts from [Proff.no](https://www.proff.no) and enter the start and end years from that table.

Then upload an Excel file in the set format.

Click 'Analyse' to analyse the data.

@@

### Transparency
```{r}
plotlyOutput("fancyplot")
```

### 2022-07-17 Shiny/Test/Test data.Rmd
Plot and explanation. ifelse() rewrite.

# Testing new data frame
if (length(unique(currency_test$valutakode)) == 1) {
  currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = "Note: not all values are denominated in the same currency")
}
```

>>>>

# Testing new data frame
if (length(unique(currency_test$valutakode)) == 1) {
  currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = "Note: not all values are denominated in the same currency")
}

# Could probably be done with two internal ifelse() functions

# ifelse() version

# Testing
currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = ifelse(length(unique(currency_test$valutakode)) == 1,
                    label_dollar(prefix = str_c(kreft_html$valutakode[1], " ")),
                    label_dollar(prefix = "? "))
      ) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = ifelse(length(unique(currency_test$valutakode)) == 1,
                         element_blank(),
                         "Note: not all values are denominated in the same currency"))

# Original
kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = ifelse(length(unique(kreft_html$valutakode)) == 1,
                    label_dollar(prefix = str_c(kreft_html$valutakode[1], " ")),
                    label_dollar(prefix = "? "))
      ) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = ifelse(length(unique(kreft_html$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
```
